---
title: "Lab 2 Team"
author: "Samuel Cole, Alicia Hauglie"
date: "2/5/2019"
output: html_document
---

github repo: https://github.com/ahauglie/DS202_lab2


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

1. What is the overall number of chocolate bars rated?
``` {r}
dim(choco)
```

1,852 chocolate bars were rated. 



2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
``` {r}
year<- choco$Review.Date
barplot(table(year))
```
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings. (Hint: They are U.S.A., France, and Canada, but find them out using codes.)
```{r}

usa<- choco[choco$Company.Location == "U.S.A.",]
france<- choco[choco$Company.Location == "France",]
canada<- choco[choco$Company.Location == "Canada",]
z <- c("USA", "France","Canada") 
boxplot(usa$Rating, france$Rating, canada$Rating, xlab="Country", ylab="Rating", main="Rating Distribution of Top 3 Countries", names = z)
```
The means are all pretty much identical, and the boxplot for Canada and USA are also very similar. This comparison shows that through the top 3 countries there is not much of a difference in Rating. 

4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.
What are the top 5 places that the cocoa beans originate from?


5. Answer the question from the dataset.
```{r}
beanOrigin <- choco$Broad.Bean.Origin
head(sort(summary(beanOrigin), decreasing=TRUE),5)
```
The top places the beans originate from are :Venezuela, Ecuador, Peru, Madagascar, Dominican Republic.

****paragraph commenting on the workflow*****