---
title: "Lab 2 Team"
author: "Samuel Cole, Alicia Hauglie"
date: "2/5/2019"
output: html_document
---

github repo: https://github.com/ahauglie/DS202_lab2


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

1. What is the overall number of chocolate bars rated?
``` {r}
dim(choco)
```

1,852 chocolate bars were rated. 



2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
``` {r}
year<- choco$Review.Date
barplot(table(year))
```
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings. (Hint: They are U.S.A., France, and Canada, but find them out using codes.)
```{r}
top3 <- choco[choco$Company.Location == "U.S.A." | choco$Company.Location == "France" | choco$Company.Location == "Canada", ]
str(top3)
boxplot(top3$Rating ~ top3$Company.Location)
top <- choco[choco$Rating %in% c("U.S.A.", "France", "Canada"),]
plot(top$Company.Location, top$Rating)

usa<- choco[choco$Company.Location == "U.S.A.",]
france<- choco[choco$Company.Location == "France",]
canada<- choco[choco$Company.Location == "Canada",]
boxplot(usa$Rating, france$Rating, canada$Rating, xlab="Country", ylab="Rating", main="Rating Distribution of Top 3 Countries")
topthree<-choco[choco$Company.Location %in% c("U.S.A.", "France", "Canada"),]
str(topthree)
boxplot(topthree$Rating~topthree$Company.Location, xlab="Country", ylab="Rating", main="Rating Distribution of Top 3 Countries", ann=TRUE)
```
4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

5. Answer the question from the dataset.



****paragraph commenting on the workflow*****